\documentclass[12pt]{beamer}

\usepackage{url}
\usetheme{Madrid}
\setbeamertemplate{footline} 

\newcommand\ans[1]{{\it ``#1''}}
%\newcommand\gap\medskip
\newcommand\gap{\vspace{5mm}}

\begin{document}

\setbeamertemplate{navigation symbols}{}

\begin{frame}
  \frametitle{Topics in statistical computing: collaborative computing and especially git}
  
\end{frame}

\begin{frame} %%%% Q1 

  \frametitle{List the collaborative scientific computing tools you have used.}

  dropbox (8), overleaf (8), github (5), Google drive (7), box (3), CVS (1), GitLab (1).
\end{frame}

\begin{frame} %%% Q2

  \frametitle{Which git topics discussed have you have already had experience with?}

  \ans{$\dots$ In the past, I have used GitHubDesktop rather than running git from the command line.}

  \gap
  
  essentially no git: 8

  \gap
  
  all the basic skills: 2
  
\end{frame}

\begin{frame}   %%% Q3

  \frametitle{Compare and contrast alternative technologies with github as platforms for collaborative statistical research.}


  \ans{While all these technologies do let you technically collaborate on files,  github seems to be uniquely suited to ease of collaboratively writing code specifically.  These other platforms are more useful for writing papers or research notes, and organizing references.}
  
\end{frame}

\begin{frame}

  \ans{GitHub is definitely the best way to share code files (or possibly a combination of codeand other files).  Git allows users to access a file’s history and see precisely which lines were changed with each update.  I’m not aware of a similar feature in either DropBox or Google Drive.  Nevertheless, I prefer OverLeaf for sharing LaTex scripts since everyone can see what changes are being made by other users in real time.}

  \end{frame}

\begin{frame}
  \ans{I  mainly  use  dropbox  for  sharing  large  files,  google  drive  are  good  for  group  writ-ing/presentation, overleaf is good for group paper writing in LaTeX. These techniquesvare good for some specific purpose, but github looks more focus on computing, with comprehensive functions.}
  
  \end{frame}

\begin{frame}
  \ans{From my perspective,  github clearly has a higher learning curve.  Dropbox does not require as much command line knowledge or careful consideration of advanced features.However, once the learning curve is overcome, github has a lot of amazing features that make it superior to other sharing software.}
  \end{frame}

\begin{frame}
  Some notes on git and github: \url{https://ionides.github.io/810f15/class12.html}
  
\end{frame}

\end{document}
